Hybrid oddball - SSVEP BCI

### 2013-07-24 draftHybridPaper/draftHybridBCI.tex
not much to say

%%%%%%%%%%%%%%%%%%%%%%%%%%%% pluses and minuses %%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%% pluses and minuses %%%%%%%%%%%%%%%

% Hybrid BCI: definition

>>>>

% pluses and minuses
Such system have been shown to work successfully on both healthy and disabled patient \cite{Sellers2010, Krusienski2008} \hl{CITE PLOS ONE PAPER}, however, as they rely on several repetition of a stimuli sequence in order to increase the signal-to-noise ratio of the \ac{ERP}, they remain slow and the communication speed decreases as the number of stimuli (\emph{i.e.} number of choices available to the user) increases.

@@

% pluses and minuses
As for oddball-based \acp{BCI}, \ac{SSVEP} systems have been successfully test on healthy subject \parencite{Friman.2007, Allison2008} and only recently (to a lesser extend) with locked-in patients \parencite{Parini2009} \hl{CITE PLOS ONE PAPER}.

on screen -> limited number of stimuli -> screen refresh rate, size of stimuli, distance between them and coamplification

% Hybrid BCI: definition
Recently, the \ac{BCI} community started to develop so-called hybrid \acp{BCI}, which combine different data acquisition techniques in order to improve the user experience of the system.
As defined by \cite{Pfurtscheller2010}, \emph{``a typical hybrid BCI is composed of one BCI and another system (which might be another BCI), and must also achieve specific goals better than a conventional system''}.
We focus here on the case where both system are \acp{BCI}.
The improvement achieved by a hybrid system can be of different natures such as a higher accuracy, number of choice or selection speed, access to a no-control state, a better usability or higher number of person effectively able to use the system \parencite{Brunner2011}.
